Optimization of respiratory syncytial virus prophylaxis using a generalized additive model of Connecticut hospitalizations

### 2018-01-15 Thesis/structure.tex
Use NEJM reference style

\usepackage[backend=bibtex,style=numeric,sorting=none,autocite=superscript]{biblatex} % Use the bibtex backend with the authoryear citation style (which resembles APA)
%\usepackage[backend=bibtex,style=authoryear,natbib=true]{biblatex} % Use the bibtex backend with the authoryear citation style (which resembles APA)

\addbibresource{Thesis.bib} % The filename of the bibliography
\renewcommand{\cite}[1]{\autocite{#1}}

>>>>

\usepackage[backend=bibtex,style=nejm,sorting=none,autocite=superscript,articledoi=true]{biblatex} % Use the bibtex backend with the authoryear citation style (which resembles APA)
%\usepackage[backend=bibtex,style=authoryear,natbib=true]{biblatex} % Use the bibtex backend with the authoryear citation style (which resembles APA)
\usepackage[nottoc]{tocbibind}

\addbibresource{../Thesis.bib} % The filename of the bibliography
\renewcommand{\cite}[1]{\autocite{#1}}
